Collaborative Visual Analysis on the Web with RCloud

### 2015-06-25 casestudies.tex
working

The result of the dimensionality reduction process is a
two-dimensional plot of the topic space, an example of which is shown in
Figure~\ref{fig:textvis}. The interactive view is implemented in SVG
and Javascript through D3~\cite{Bostock:2011:DDD}. One of the most
popular web-based visualization libraries for R is ggvis~\cite{ggvis},
so it is natural to ask if ggvis could have been used instead of
custom Javascript. In this case, the interactive features of ggvis
(and, by extension, Shiny) are a subset of those in Vega~\cite{vega}.
Custom interactions in LDAVis (such as hovering over a topic,
topic cluster, or word) do not appear to be available yet in Vega~\cite{vega},
although the required components for reactive interaction were
recently described by Satyanarayan et
al.~\cite{Satyanarayan:2014:DID}.
Although custom Javascript was required, its flexibility is welcomed
by many web developers.

LDAVis highlights some unique features of RCloud.
While RCloud notebooks allow deployment of R analyses over
the web with no additional effort, RCloud \emph{applications} are more
powerful, and are developed with a combination of Javascript and HTML
for the front end. This requires additional knowledge over Shiny, but
the RCloud model makes analysis simpler (since analysts
simply write R in the style they already know)
and front end visualization side is simpler for web
developers (since they simply write Javascript in
the style \emph{they} know). In addition, RCloud applications
inherit the automatic deployment and discoverability features of
all RCloud notebooks.

>>>>

The result of the dimensionality reduction process is a
two-dimensional plot of the topic space, an example of which is shown in
Figure~\ref{fig:textvis}. The interactive view is implemented in SVG
and Javascript through D3~\cite{Bostock:2011:DDD}. One of the most
popular web-based visualization libraries for R is ggvis~\cite{ggvis},
so it is natural to ask if ggvis could have been used instead of
custom Javascript. In this case, the interactive features of ggvis
and Shiny are a subset of Vega's~\cite{vega}.
Custom interactions in LDAVis (like hovering over a topic,
topic cluster, or word) are not available yet in Vega~\cite{vega},
although the required components were recently described by Satyanarayan et
al.~\cite{Satyanarayan:2014:DID}.
Although LDAVis required custom Javascript, that flexibility is welcomed
by many web developers.

LDAVis demonstrates some unique features of RCloud.
While RCloud notebooks allow deployment of analyses over
the web with no extra effort, RCloud \emph{applications} are more
powerful, and are developed by combining Javascript and HTML
for the front end. This requires more expertise than Shiny, but
the RCloud model makes analysis simpler (since analysts
simply write R in the style they already know)
and the visualization front end is simpler for web
developers (since they simply write Javascript in
the style \emph{they} know).
LDAVis inherits the automatic deployment and discoverability
of all RCloud applications.
% In addition, RCloud applications
% inherit the automatic deployment and discoverability features of
% all RCloud notebooks.
